---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---


```{r fig.height=7, fig.width=11}
library(tidyverse); library(here)
log_all_clean <- readRDS(here("/data/log_all.RDS"))


ggplot(log_all_clean, aes(created_dt, parse_number(Pos), group = Musher)) +
  geom_line(color = "gray70") +
  
  geom_line(data = log_all_clean %>%
              filter(Musher %>% str_detect("Petit"))) +
  geom_line(data = log_all_clean %>%
              filter(Musher %>% str_detect("Kais")),
            color = "red") +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%a\n%m/%d", minor_breaks = NULL) +
  scale_y_reverse() 

```

```{r}

# convert_time <- function(dt) {
#   tempDate = lubridate::ymd(paste("2019",str_sub(dt, end = 4) %>% str_trim()))
#   tempDT = lubridate::ymd_hms(paste(tempDate, str_sub(dt, start = 4)))
# }


locations <- log_all_clean2 %>%
  group_by(Checkpoint) %>%
  summarize(firstIn = min(InTime2, na.rm = T)) %>%
  arrange(firstIn) %>%
  mutate(Checkpoint = fct_reorder(Checkpoint, firstIn))

ggplot(locations, aes(firstIn, Checkpoint)) + geom_point()

ggplot(locations, 
       aes(InTime, OutTime, label = Musher)) +
  geom_text() +
  facet_wrap(~Checkpoint)


```



Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

